The variability of Betelgeuse explained by surface convection

### 2024-01-30 main.tex
Corrected bib
sect 2

>>>>

In this work we shall look into the signals produced through these line-addition techniques, and which produce a pseudo-spectral line in intensity 
and linear polarization which does not belong to any atomic species in particular but to an average of all of them present and emitting in the 
photosphere of Betelgeuse. These signals carry the coherent signals present in the photospheric lines, but the particularities of this or 
that spectral line are erased. All these data has been presented before by \cite{auriere_discovery_2016}, \cite{mathias_evolution_2018} and 
\cite{lopez_ariste_three-dimensional_2022}, which also give details on observing times and conditions as well as more detailed description 
on the data reduction \footnote[1]{Beyond a 2-year proprietary embargo, and up to technical issues, all these data is available through 
PolarBase (http://polarbase.irap.omp.eu/).}
